Homelessness in Toronto: A Solvable Social Issue

### 2023-04-20 outputs/paper/paper.qmd
final paper

---
title: "Toronto's Homeless: Understanding the Causes and Seeking Solutions"
subtitle: "Homelessness "
author: 
  - Will Davidson
thanks: "Code and data are available at: https://github.com/willdavidson01/Toronto-Homeless"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "People suffering from homelessness in the City of Toronto have become an accepted part of the urban landscape.  With the shortage of affordable housing, high rents, poor economy and rising mental health concerns, it’s hard to imagine a viable solution to this critical social determinant of health.  Using OpenDataToronto, this paper analyzes data and identifies trends in different populations, gender, and age, as well as the current capacity to house people either in an emergency or permanent housing. It also challenges current assumptions and draws attention to the fact that today’s data can provide solutions to tomorrow’s needs."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Homelessness in Toronto: A Solvable Social Issue"
subtitle: "Root Causes, Insights and Data-driven Strategies"
author: 
  - Will Davidson
thanks: "Code and data are available at: https://github.com/willdavidson01/Toronto-Homeless"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "People suffering from homelessness in the City of Toronto have become an accepted part of the urban landscape.  With the shortage of affordable housing, high rents, poor economy and rising mental health concerns, it’s hard to imagine a viable solution to this critical social determinant of health.  Using OpenDataToronto, this paper analyzes data and identifies trends in different populations, gender, and age, as well as the current capacity to house people either in an emergency or permanent housing. It also challenges current assumptions and draws attention to the fact that today’s data can provide solutions to tomorrow’s needs."
format: pdf
number-sections: true
bibliography: references.bib
---
